\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{titling}
\usepackage{tikz}

\title{\huge{English Assignment 5 Listening Skills\\\hspace{7cm}- Usha Mahadevan}
}
\author{Soham Chatterjee\\Roll: BMC202175}
\date{}
\setlength{\parindent}{1cm}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}
\begin{document}
	\maketitle\pagebreak
	\textbf{Question:} How does the author bring out the trauma of Seita in Grave of the Fireflies 
	
	
	\textbf{Answer:} In the movie Grave of the Fireflies or Hotaru No Haka made by Studio Ghibli we see the tragic story of two characters, the main character, a young boy Seita and his little sister Setsuko. The author brings out the trauma of Seita in many different situations through out the story.
	
	He fears because of his bad decisions his little sister is suffering. We can see a sign of regret when the spirit is repenting on the decision of letting his aunt sell his mother's kimono and without listening to setsuko's crying. He feels a great regret upon hurting setsuko. 
	
	The movie does not show much about seita's mental state upon seeing his mother's death so that he does not make setsuko feel sad. But when he saw setsuko is making a grave for her mother he broke into tears. Which really shows how the war is making him weak mentally. 
	
	When they left his aunt's house they started to live under an abandoned shelter. We can see his spirit is regretting - what if that day he didn't let his pride take the decision her sister would grow up healthy.  
	
	He started stealing stuff from houses when it is getting bombered so that he can buy all the things setsuko wants. When he got caught and in front of police station he met his little sister he was ashamed of himself. After the check up setsuko says that she wants his brother to be with her and nothing more, no good food only his brother. Seita after that withdraws all the money from bank to give setsuko good food but it was late. He regrets that decision till his death - why he didn't withdrew the money earlier. 
	
	All these things brings out seita's trauma which makes the audience brake into cry. THe tragic death of the whole seita's family is represented as fireflies and setsuko asks "Why do fireflies die so soon?"
	
	
\end{document}