\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{titling}
\usepackage{tikz}

\title{\huge{English Assignment 2\\\hspace{7cm}- Usha Mahadevan}
}
\author{Soham Chatterjee\\Roll: BMC202175}
\date{}
\setlength{\parindent}{1cm}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}
\begin{document}
	\maketitle\pagebreak
	\textbf{Question:} Imagine you are Philip making a diary entry.  Write in about 200 words how you expected the meeting with Uncle James to turn out and how it turned out eventually. Focus the writing on your thoughts and emotions.
	
	\textbf{Answer:} Those four years  were not so easy. Now it is immeasurable peace to get up little late in the morning. Though I had to remain hungry  for some time. But in the mean time I visited Aunt Emily. She is the most caring person I had seen in my life. She suddenly talked about Uncle James while we were having a conversation. Uncle James was always very strict and rude with me. I was worrying how he will react to my late getting up. Aunt Emily asked me to meet Uncle James and she told me that Uncle James is waiting for me. That got me pretty worried. However I went to the dining room to have my breakfast. Uncle was asleep in front of the fire. When I was halfway done he woke up and he didn't react to my being late for breakfast, instead he laughed. We started talking quite frankly. Though he shivered when I took out my pipe but didn't oppose me when I asked if I Could smoke. He was taking strangely like if I wanted to become an architect. He then asked me if I would join his jam business. Though I had no problem but it seemed that Uncle James didn't expected me to reply that. In short the whole conversation was completely opposite to his usual character.
\end{document}