\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{titling}
\usepackage{tikz}

\title{\huge{English Assignment 3\\\hspace{7cm}- Usha Mahadevan}
}
\author{Soham Chatterjee\\Roll: BMC202175}
\date{}
\setlength{\parindent}{1cm}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}
\begin{document}
	\maketitle\pagebreak
	\textbf{Question:} Give any three qualities in Martin Luther King that enables him to emerge as a powerful  leader and illustrate with the help of the text prescribed.
	
	\textbf{Answer:} In the biography of Martin Luther King Jr. written by Coretta S. King we can say many characteristics of Martin Luther King Jr. which makes him as a powerful leader. Here we will discuss 3 of his such qualities.
	
	Firstly the way he inspires others with his speech. Through out the biography we can see he always says to love their enemies, their path is guided by Jesus -- which makes everyone inspires every black people as their path is not lead by hatrade. Also he says "Let your conscience be your guide." which psychologically makes everyone to follow the path they are taking.
	
	He prevents his followers from taking the path of violence. When the narrator's house was bombed a big crowd collected in front of his house with armed weapons. Martin Luther King Jr. gave a speech preventing them to take any step towards violence instead he calmed the people by saying that they are following the path of Jesus and they should love all white men. With that the crowed began to thin out and people started to go home. Even the white policeman said "If it hadn't been for the nigger preacher, we'd all be dead." 
	
	He is very much tolerant. He got arrested because of going over speed limit, his house got bombed, he got arrested again but he neither wavered in his decision of the Montgomery Movement nor he used all that to make his people do revengeful actions against the white people.
	
	All these qualities make Martin Luther King Jr. a powerful leader.

\end{document}