\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{titling}
\usepackage{tikz}

\title{\huge{English Assignment 4\\\hspace{7cm}- Usha Mahadevan}
}
\author{Soham Chatterjee\\Roll: BMC202175}
\date{}
\setlength{\parindent}{1cm}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}
\begin{document}
	\maketitle\pagebreak
	\section*{1. Julius Caesar}
	In Shakespeare's ``The Tragedy of Julius Caesar",  the main character of the play, Julius Caesar appeared for a very short time. But through that short appearance we get to see some characteristics.
	
	At first there was a huge crowd had gathered to see Caesar who was returning victorious. This scene shows how much impact Caesar has over the common people of Rome. Which shows how many people respects and honors him.
	
	In the speech of Antonio after the death of Caesar we get to see Caesar brought back many captives home, when the poor people cried Caesar's eyes also became tearful. Even on the Lupercal when Antonio presented crown three times Caesar refused every time. This shows how much generous, selfless, person he is and we saw his great capabilities as a leader.
	
	We also see Caesar being insecure over Cassius. He describes him as ``lean and hungry" which is infact true. This shows he can see through anyone's's false appearance and find his true characteristics.
	
	All this characteristics can be found though his short appearance in the play.

		
	\section*{2. Mark Antony}
	In Shakespeare's ``The Tragedy of Julius Caesar", we saw very short glimpses of Antony in Act 1 Scene 2 but in the Act 3 scene 2 his characteristics come out very well. He appears in Act 3 scene 2 with Caesar's body. the conspirators who were led by Brutus had allowed Antony to give a speech to express is grief to the common citizen of Rome.
	
	Through the speech he marks out many cases where he shows Caesar's greatness by contradicting Brutus' words. He refers to Brutus' accusation that ``Caesar was ambitious", acknowledges that he speaks with ``honorable". ``For Brutus is an honorable man, / So are they all, all honorable men" or ``But Brutus says he was ambitious, / And Brutus is an honorable man." - he phrase is repeated four times, in slightly variant forms, allowing Antony not only to counter each of Brutus' arguments, but also question Brutus' honor simply by drawing so much attention to it. Even though people were cheering Brutus and were happy that Rome got rid of Caesar Antony didn't hesitate to counter Brutus's Words and question his honor. This shows that Antony was shrewd and no matter what he does not leave his friend's side.
	
	Antony wanted to seek revenge over his friend's death but at the same he also wanted to gain public sympathy. He told them that they have lost their judgmental powers. They all loved Caesar once then what was holding them to mourn for Caesar. Thus he encourages the public  to feel sorrow for Caesar's death and question the honorable people.
	
	Then Antony mentioned how dearly Caesar loved Brutus by mentioning ``For Brutus, as you know, was Caesar’s angel". Then by saying how deeply Caesar was wounded seeing Brutus stab Antony made a fire of seeking revenge in the hearts of citizen. They all were very desperate to kill the traitor.
	
	Then Antony proceed to read the will. He read aloud that Caesar had given all his property for the sake of common people. This led the common people's rage to revenge of death of Caesar and killing of Brutus.
	
	
	
\end{document}