\begin{rubric}{Talks and Presentations}
\entry*[2026]%
    \textbf{$\mathsf{BPL}\subseteq\mathsf{SC}$: Nisan's Pseudorandom Generator for $\mathsf{BPL}$}

    Course-Work presentation (TIFR): Pseudorandomness. Paper by Noam Nisan, 1992

    Slides: [\href{https://sohamch08.github.io/assets/nisan-rl-prg.pdf}{PDF}]

\entry*[2026]%
    \textbf{Subspace Polynomials and List Decoding of Reed Solomon Codes}
    
    Course-Work presentation (TIFR): Topics in Coding Theory. Paper by Eli Ben-Sasson, Swastik Kopparty \& Jaikumar Radhakrishnan, 2006.

\entry*[2026]%
    \textbf{Universal Optimality of Dijkstra using Fibonacci Priority Queue with Working Set Property}

    Oral Qualfier Presentation. Paper by Haeupler, Hladík, Rozhoň, Tarjan, Tětek, 2024. FOCS Best Paper.

    Slides: [\href{https://sohamch08.github.io/assets/dijkstra-optimal.pdf}{PDF}]
\entry*[2026]%
    \textbf{$n^{1.62}$ Upper Bound of the Hurwitz Problem}

    TIFR Student Seminar. Paper by Pavel Hrubesh, 2024
\entry*[2025]%
    \textbf{Super Polynomial Lower Bound on Traveling Salesman Polytope}

    Coursework Presentation (TIFR): Combinatorial Optimization. Paper by Fiorini, Massar, Pokutta, Tiwary and Wolf, 2012

    Slides: [\href{https://sohamch08.github.io/assets/copt-presentation.pdf}{PDF}]
 \entry*[2025]%
    \textbf{Bounds on Price of Anarchy using LInear and Quadratic Programming}

    Coursework Presentation (TIFR): Algorithmic Game Theory. Paper by Kulkarni and Mirrokni, 2015.

    Slides: [\href{https://sohamch08.github.io/assets/agt-presentation.pdf}{PDF}]
\entry*[2025]%
	\textbf{Bipartite Matching is in \textsf{Quasi-NC}}

    TIFR Student Seminar. Paper by Stephen A. Fenner, Rohit Gurjar and Thomas Thierauf, 2016.
\entry*[2024]%
	\textbf{Hensel and Newton Methods in Valuation Rings}

    Coursework Presentation (CMI): Algebra and Computatiopn. Paper by J von zur Gathen, 1984
\entry*[2023]%
	\textbf{Coursework Presentation (Algorithmic Coding Theory II)}

    Algebraic Geometric Codes, jointly presented by Me and Shree Ganesh S J

    Report: [\href{https://sohamch08.github.io/assets/act-report.pdf}{PDF}]
\entry*[2023]%
	\textbf{Coursework Presentation (Parallel Algorithms anc Complexity)}

    ``Iterated Mod Problem" by Karloff and Ruzzo

    Slide: [\href{https://sohamch08.github.io/assets/parallel-presentation-iterated-mod.pdf}{PDF}]
\end{rubric}