\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{fullpage} % changes the margin
\usepackage[a4paper, total={7in, 10in}]{geometry}
\usepackage{amsmath,mathtools,mathdots}
\usepackage{amssymb,amsthm}  % assumes amsmath package installed
\usepackage{float}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue!70!red,
	pdftitle={Assignment}, %%%%%%%%%%%%%%%%   WRITE ASSIGNMENT PDF NAME  %%%%%%%%%%%%%%%%%%%%
}
\usepackage[most,many,breakable]{tcolorbox}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,angles,quotes,patterns}
\usepackage{caption}

\definecolor{mytheorembg}{HTML}{F2F2F9}
\definecolor{mytheoremfr}{HTML}{00007B}


\tcbuselibrary{theorems,skins,hooks}
\newtcbtheorem{problem}{Problem}
{%
	enhanced,
	breakable,
	colback = mytheorembg,
	frame hidden,
	boxrule = 0sp,
	borderline west = {2pt}{0pt}{mytheoremfr},
	sharp corners,
	detach title,
	before upper = \tcbtitle\par\smallskip,
	coltitle = mytheoremfr,
	fonttitle = \bfseries\sffamily,
	description font = \mdseries,
	separator sign none,
	segmentation style={solid, mytheoremfr},
}
{p}

% To give references for any problem use like this
% suppose the problem number is p3 then 2 options either 
% \hyperref[p:p3]{<text you want to use to hyperlink> \ref{p:p3}}
%                  or directly 
%                   \ref{p:p3}



\input{letterfonts}

\input{macros}

\setlength{\parindent}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\textsf{\noindent \large\textbf{Soham Chatterjee} \hfill \textbf{Assignment - 1}\\
		Email: \href{sohamc@cmi.ac.in}{sohamc@cmi.ac.in} \hfill Roll: BMC202175\\
		\normalsize Course: Parallel Algorithms and Complexity \hfill Date: August 16, 2023}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Problem 1
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{problem}{%problem statement
		}{p1% problem reference text
		}
		$ITERADD_{poly(\log n),n}\in AC^0$ where $ITERADD_{poly(\log n),n}$ is problem of adding polylog many $n$-bit numbers.
		
		%Problem		
	\end{problem}
	
	\solve{
		%Solution
		We already know $ITERADD_{\log n,n}\in AC^0$. So we will use this in order to show $${ITERADD_{poly(\log),n}\in AC^0}$$Number of bits after adding $k$ many $n$-bit numbers is $\log k+n$ bits. We will solve it with a tree like circuit with depth $k$.
		
		Suppose we are given $\log^k n$ many $n$-bit numbers. Let the numbers are $a_1,\dots,a_{\log^kn}$. Now we group the numbers where each group contains $\log n$ many numbers. So there will be total $\log^{k-1}n$ many groups. In each group we will add the $\log n$ many $n$-bit numbers which we know we can do in $AC^0$. Now from each group we get  numbers with $\log \log n+n=O(n)$ bits.
	
		
		Now from these $\log^{k-1}n$ many $O(n)$ bits numbers we again form groups where each group contains $\log n$ many numbers. So we will have $\log ^{k-2}n$ many groups. Again in each group we add the $\log n$ many $n$ bit numbers which we can do in $AC^0$. The numbers we get from each group has $\log\log n+O(n)=O(n)$ bits. 
		
		We continue this and notice each time the power of the $\log$ is reducing by 1. So we have to do this process $k$ times. And then we will have 1 number which is the addition of all the $\log^kn$ many $n$-bit numbers. In $i$-th step we use the $AC^0$ circuit for adding $\log n$ many $n$-bit numbers and get $\log^{i-1}n$ numbers where each number has $\log\log n+O(n)=O(n)$ many bits.
		
		Since each step is using a $AC^0$ cicruit parallely $\log^{i-1}n$ many times and there are total $k$ many such iterations. So the total circuit will have constant depth and polynomial size. Hence $ITERADD_{poly(\log n),n}\in AC^0$
		
		
	}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Problem 2
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\begin{problem}{%problem statement
		}{p2% problem reference text
		}
		%Problem	
		\textbf{Defintiion 1:} It is the class of constant depth polynomial size circuits with AND, OR, NOT, MAJORITY gates.	\parinf
		
		\textbf{Defintiion 2:} It is the class of constant depth polynomial size circuits with  NOT, MAJORITY gates.	
		\vspace*{5mm}
		
		Equivalence of The two Definitions of $TC^0$
	\end{problem}
	
	\solve{
		%Solution
		If we can construct the AND and OR gate with MAJORITY gate in constant depth and polynomial size then we can say these two definitions are equivalent.
		
		Now if $a_0,\dots,a_{n-1}$ are $n$ bits. Then $$\bigwedge_{i=0}^{n-1}a_i=MAJORITY\Big(a_0,\dots,a_{n-1},\underbrace{0,0,\dots,0}_{n-1\text{ times}}\Big)$$Similarly
		$$\bigvee_{i=0}^{n-1}a_i=MAJORITY\Big(a_0,\dots,a_{n-1},\underbrace{1,1,\dots,1}_{n-1\text{ times}}\Big)$$
		Now the AND and OR gate both can be replaced with $O(1)$ depth $O(n)$ size  subcircuits using only MAJORITY gates in a circuit and still the total depth of the circuit will be constant and size is polynomial. 		Hence the two definitions are equivalent.
	}
	
	
	
	
\end{document}
