\chapter{Mean Value Theorem}
We will use Euclidean norm on $\bbR^n$ and have Cauchy-Schwarz Inequality $|v\cdot w|\leq \|v\|\|w\|$.
\begin{theorem}{1-Variable MVT}{1varmvt}
	If $f:[a,b]\to \bbR$ continuous and $f'$ exists on $(a,b)$, then $\exists7 c\in(a,b)$ s.t $$f(a)-f(b)=f'(c)(b-a)$$
\end{theorem}
\begin{myproof}1-variable MVT

	\hspace{1cm} $\Uparrow$ Via Rolle's Theorem, using $f'(\text{extremum})=0$

	\hspace*{0.5cm}Extreme Value Theorem

	\hspace{1cm} $\Uparrow$ $[a,b]$ is compact, $f$ is continuous $\implies f([a,b])$ is compact in $\bbR\implies $ closed and bounded

	\hspace*{0.5cm}Heine Borel Theorem
\end{myproof}

\qs{}{First consider $f:[a,b]\to\bbR^n$ continuous and $f'$ exists on $(a,b)$. Is there a $c\in (a,b)$ s.t. $$\|f(b)-f(a)\|\overset{?}{=}\|f'(c)\|(b-a)$$}
\solve{No. For example $f:[0,2\pi]\to\bbR^2$ which maps $t\mapsto (\sin t,\cos t)$. Then $f'(t)=(\cos t,-\sin t)$ and $\|f'(t)\|=1$. $f(2\pi)-f(0)=(0,0)$}
\begin{theorem}{MVT of Real-Valued Functions}{}
	Let $f$ be a continuous function $[a,b]\to \bbR^n$ and $f'(c)$ exists $\forall\ c\in(a,b)$. Then $\exs\ c\in (a,b)$ s.t $$\|f(b)-f(a)\|\leq (b-a)\|f'(c)\|$$(Here the norm is Euclidean norm. For the inequality which norm we take does matter.)
\end{theorem}
\begin{myproof}
	Clever use if \hyperref[th:1varmvt]{$1-$Variable MVT}. We want to bound norm of $f(b)-f(a)=z$.\parinf

	\textbf{Idea: }Dot with $z$ and then use Cauchy Schwarz \parinn
	\begin{center}
		\begin{tikzcd}
			{[a,b]} \arrow[r, "f"]                                     & \mathbb{R}^n \arrow[r, "{g=\langle -,z\rangle}"] & \mathbb{R}              \\[-0.7cm]
			t \arrow[r, maps to] \arrow[rr, "\phi(t)"', bend right=49] & f(t) \arrow[r, maps to]                        & {\langle f(t),z\rangle}
		\end{tikzcd}
	\end{center}
	Notice $g: \bbR^n\to\bbR$ where $g$ maps $x\longmapsto \langle x,z\rangle=x_1z_1+\cdots+x_nz_n$. Hence $g$ is differentiable and $g'(x)=\lt[ \begin{matrix} z_1 & z_2 & \cdots & z_n\end{matrix}\rt]$. Now we can apply $MVT$ to $\phi$. $$\phi(b)-\phi(a)=(b-a)\phi'(c)$$\begin{align*}
		LHS & =\phi(b)=\phi(a)                                       \\
		    & =\langle f(b),z\rangle -\langle f(a),z\rangle          \\
		    & =\langle f(b)-f(a),z\rangle=\langle z,z\rangle=\|z\|^2
	\end{align*}And$$\phi'(c)=(g\circ f)'(c)=g'(f(c))\circ f'(c)=\langle z ,f'(c)\rangle$$Therefore$$\|z\|^2=\langle z,f'(c)\rangle\leq (b-a)\|z\|\|f'(c)\|$$Nothing to prove if $\|z\|=0$ and else cancel $\|z\|$ from both sides.
\end{myproof}
\begin{theorem}{General Multivariable MVT}{}
	Let $\bbR^m\supset \text{Convex Open }U\xrightarrow{f}\bbR^n$, $ f$ differentiable on $U$ and $ \|f'(x)\|<M \ \forall\ x\in U$. Then $\forall\ a,b\in U$ $$\|f(b)-f(a)\|\leq M\|b-a\|$$
\end{theorem}
\begin{myproof}
	Given $a,b\in U$ holds $\gamma:[0,1]\to U$ which maps $t\to a+t(b-a)$ [This is valid by convexity]. Apply MVT to
	\begin{center}
		\begin{tikzcd}[every label/.append style={font=\normalsize}]
			{[0,1]} \arrow[r, "\gamma"] \arrow[rr, "g"', bend right] & U \arrow[r, "f"] & \bbR^n\\[-0.7cm]
		\end{tikzcd}
	\end{center}
	We get $\in(0,1)$ such that $\|g(1)-g(0)\|\leq \|g'(t)\|$ i.e $$\|f(b)-f(a)\|\leq \| \underbrace{f'(\gamma(t))\circ \gamma'(t)}_{\substack{ \text{Matrix Vector} \\ \text{Multiplication} }} \| \underbrace{\leq}_{\substack{\downarrow \\ \text{Justify}}}  M\|b-a\|$$
\end{myproof}

Suppose $U$ is convex in $\bbR^m$, $f:U\to \bbR^n$ and $f'(a)=0$ $\forall\ a\in U$. Then $f=$ Constant because $$\|f(b)-f(a)\|\leq 0\|b-a\|$$ $\forall\ a,b\in U$ by MVT. What happens if $U$ is open but not convex. If $U$ is connected the conclusion is again true.
\dfnc{Connected Set in $\bs{\bbR^n}$}{
	A set $S$ in $\bbR^n$ is (path)connected if $\forall \ a,b\in S$ $\exs$ continuous function
	\begin{center}
		\begin{tikzcd}[ampersand replacement = \&]
			{\gamma} \&[-1cm] [0,1] \arrow[r] \& S\\[-0.7cm]
			\& 0 \arrow[r, mapsto] \& a\\[-0.7cm]
			\& 1 \arrow[r, mapsto] \& b
		\end{tikzcd}
	\end{center}
}
\begin{theorem}{}{}
	If $S$ is connected open set in $\bbR^n$ and $f:S\to \bbR^n$ is differentiable on $U$  with $f'(a)=0$ $\forall \ a\in U$ then $f(a)=$ Constant.
\end{theorem}
\begin{myproof}
	$\forall\ x\in \gamma([0,1])$ find $B_r(x)\subset S$. $\gamma([0,1])$ is compact. So $\exs$ finite subcover of $\gamma([0,1])$ by balls around $\gamma(t_1),\gamma(t_2),\dots,\gamma(t_N)$.

	Order these alls so that $a\in $ first ball and $b\in$ last ball, any two consecutive balls overlap. This gives piecewise linear path from $a\to b$. Use MVT for each segment.
\end{myproof}
